---
title: "Midpoint Deliverable"
output: html_document
---
```{r include = FALSE}
source("scripts/aggregateTableScript.R")
source("scripts/summaryInformation.R")
library(knitr)
```
### Introductory paragraph
Sports are one of the many things that help connect people and communities across the globe. We're interested in making use of this open dataset so people can grow their appreciation and understanding of sports. Providing this kind of data can help improve player performance and encourage fans to attend games.

### Summary Paragraph
```{r echo = F}
info <- get_summary_info(athlete_events)
```
The dataset we used had all sorts of data ranging from `r info$oldest_data` to `r info$newest_data`. 

### Table
Render your table and describe pertinent observations found in it
Some obersvations we found inside our aggregated table

rm(df)
```{r echo = F}
df <- aggregate_info(athlete_events)
kable(df)
```

### Purpose
Describe the purpose of each chart (e.g., "this chart was intended to show the relationship between..."), render each chart, and describe pertinent observations found in each chart

**Chart 1**
```{r echo = F}

```

**Chart 2**
```{r echo = F}

```

**Chart 3**
```{r echo = F}

```